sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-03 doc/paper.Rmd
Add a rough future directions paragraph

Additional functionality and future directions here?

@@

@@

@@

>>>>

Additional functionality in sdmTMB not already mentioned includes interpolating across missing time slices and forecasting, spatial covariance barriers, time-varying spatiotemporal variance, and simulation from the parameter joint precision matrix.
Future development may include zero-inflated models, improvements to Bayesian sampling efficiency, continuous time models, and non-gaussian random fields (REF).
We may introduce explicit delta models, but many such models can already be fit with sdmTMB by modelling the two components separately.
We may introduce capability for multivariate response data, but VAST already focusses on such models with a TMB backend. Furthermore, we would only add this functionality if we could maintain a straightforward interface for univariate data.

@@

TODO
Would not be possible without TMB and INLA.
Heavily inspired by and in some places code has been adapted from VAST and glmmTMB...

@@

None?

@@

TODO
